\textbf{Teaching a machine to generate an artificial universe}

### 2020-10-14 paper.tex
minor fix of line ending

The webbed structure is native to the well-established $\Lambda$ Cold Dark Matter ($\Lambda \text{CDM}$) cosmology but 
its exact origins are not well understood~\cite{class_perturbs} and at present it is believed that the structure originates 
from an amplification of quantum fluctuations as a density perturbation in the early universe~\cite{perturbation_theory}, 
which is described by inflationary cosmology~\cite{inflation_cosmology}. The matter distribution of webbed structure in 
the universe holds information on the true nature of dark matter, dark energy, the laws of gravity and the mode of galaxy 
formation~\cite{DarkEnergySurvey, kids_lensing, kids_cosmo, gal_formation, gal_formation2}.

>>>>

The webbed structure is native to the well-established $\Lambda$ Cold Dark Matter ($\Lambda \text{CDM}$) cosmology but 
its exact origins are not well understood~\cite{class_perturbs} and at present it is believed that the structure originates 
from an amplification of quantum fluctuations as a density perturbation in the early universe~\cite{perturbation_theory}, 
which is described by inflationary cosmology~\cite{inflation_cosmology}. The matter distribution of webbed structure in 
the universe holds information on the true nature of dark matter, dark energy and the~mode~of~galaxy~ 
formation~\cite{DarkEnergySurvey, kids_lensing, kids_cosmo, gal_formation, gal_formation2}.
